Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-09-30 Paper.tex
The citations were rendering with a ?, so I fixed that by checking the output, finding that there were three errors with cross-references and fixed them. I also fixed some syntax for the Ethash functions, which while they haven't caused the build to fail, isn't good practice to have _\mathrm, so I changed this to _{\mathrm} and also fixed a couple of other errors.

The values stemming from the computation of transactions, specifically the \hyperlink{transaction Receipt}{transaction receipts, $B_\mathbf{R}$}, and that defined through the transaction's \hyperlink{Pi}{stateR-accumulation function, $\Pi$}, are formalised later in section \ref{sec:statenoncevalidation}.

@@

The validity is determined as:
\begin{equation}
\begin{array}[t]{rcl}
S(T) & \neq & \varnothing \quad \wedge \\
\boldsymbol{\sigma}[S(T)] & \neq & \varnothing \quad \wedge \\
T_\mathbf{n} & = & \boldsymbol{\sigma}[S(T)]_\mathbf{n} \quad \wedge \\
g_0 & \leqslant & T_\mathbf{g} \quad \wedge \\
v_0 & \leqslant & \boldsymbol{\sigma}[S(T)]_\mathbf{b} \quad \wedge \\
T_\mathbf{g} & \leqslant & {B_H}_\mathbf{l} - \hyperlink{ell}{\ell}\hyperlink{R u}{(B_\mathbf{R})_\mathbf{u}}
\end{array}
\end{equation}

@@

There exists a seed which can be computed for each block by scanning through the block headers up until that point. From the seed, one can compute a pseudorandom cache, \hyperlink{Jcacheinit}{$J_{\mathrm{cacheinit}}$} bytes in initial size. Light clients store the cache. From the cache, we can generate a dataset, \hyperlink{Jdatasetinit}{$J_{\rm{datasetinit}}$} bytes in initial size, with the property that each item in the dataset depends on only a small number of items from the cache. Full clients and miners store the dataset. The dataset grows linearly with time.

@@

\begin{tabularx}{\textwidth}{lrX}
%\begin{tabu}{X[,l]X[,r]X[,l]} 
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{} \\
\midrule 
$J_\mathrm{wordbytes}$ & 4  & This is the bytes in a word. \hypertarget{Jdatasetinit}{} \\
$J_\mathrm{datasetinit}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{} \\
$J_\mathrm{datasetgrowth}$ & $2^{23}$ & This is the dataset growth per epoch.  \hypertarget{Jcacheinit}{\\
$J_\mathrm{cacheinit}$ & $2^{24}$ & This is the bytes in the cache at genesis.}\hypertarget{Jcachegrowth}{\\
$J_\mathrm{cachegrowth}$ & $2^{17}$ & This is the cache growth per epoch.}\hypertarget{Jepoch}{\\
$J_\mathrm{epoch}$ & 30000 & This is the blocks per epoch.}\hypertarget{Jmixbytes}{\\
$J_\mathrm{mixbytes}$ & 128 & This is the mix length in bytes.}\hypertarget{Jhashbytes}{\\
$J_\mathrm{hashbytes}$ & 64 & This is the hash length in bytes.}\hypertarget{Jparents}{\\
$J_\mathrm{parents}$ & 256 & This is the number of parents of each dataset element.}\hypertarget{Jcacherounds}{\\
$J_\mathrm{cacherounds}$ & 3 & This is the number of rounds in cache production.}\hypertarget{Jaccesses}{\\
$J_\mathrm{accesses}$ & 64 & This is the number of accesses in a hashimoto loop.}\\
\bottomrule
%\end{tabu}
\end{tabularx}

\subsection{Size of dataset and cache}
The size for Ethash's cache $\mathbf{c} \in \mathbb{B}$  and dataset $\mathbf{d} \in \mathbb{B}$ depend on the epoch, which in turn depends on the block number.
\begin{equation}
E_{\mathrm{epoch}}(\hyperlink{H i}{H_\mathbf{i}}) = \left\lfloor\frac{\hyperlink{H i}{H_\mathbf{i}}}{\hyperlink{Jepoch}{J_\mathrm{epoch}}}\right\rfloor
\end{equation}
The size of the dataset growth is \hyperlink{Jdatasetgrowth}{$J_\mathrm{datasetgrowth}$} bytes, and the size of the cache growth is \hyperlink{Jcachegrowth}{$J_{\mathrm{cachegrowth}}$} bytes, where the growth of each occurs every epoch. In order to avoid regularity leading to cyclic behavior, the size must be a prime number. Therefore the size is reduced by a multiple of \hyperlink{Jmixbytes}{$J_{\mathrm{mixbytes}}$}, for the dataset, and \hyperlink{Jhashbytes}{$J_{\mathrm{hashbytes}}$} for the cache.\hypertarget{dsize}{
Let $d_{size} = \lVert \mathbf{d} \rVert$ be the size of the dataset. Which is calculated using:}
\begin{equation}
 d_{size} = E_{prime}(\hyperlink{Jdatasetinit}{\hyperlink{Jdatasetinit}{J_{\mathrm{datasetinit}}}} + \hyperlink{Jdatasetgrowth}{J_{\mathrm{datasetgrowth}} \cdot E_{\mathrm{epoch}} - \hyperlink{Jmixbytes}{J_\{rm{mixbytes}}}, J_{\mathrm{mixbytes}})
\end{equation}
The size of the cache, $c_{size}$, is calculated using
\begin{equation}
 c_{size} = E_{prime}(\hyperlink{Jcacheinit}{J_{\mathrm{cacheinit}}} + \hyperlink{\mathrm{cachegrowth}}{J_{\mathrm{cachegrowth}}} \cdot E_{\mathrm{epoch}} - \hyperlink{Jhashbytes}{J_{\mathrm{hashbytes}}}, J_{\mathrm{hashbytes}})
\end{equation}
\begin{equation}
 E_{prime}(x, y) = \begin{cases}
x & \text{if} \quad x / y \in \mathbb{P} \\
E_{prime}((x - 1) \cdot y, y) & \text{otherwise}
\end{cases}
\end{equation}
\subsection{Dataset generation}
In order the generate the dataset we need the cache $c$, which is an array of bytes. It depends on the cache size  $c_{size}$ and the seed hash $s \in \mathbb{B}_{32}$.
\subsubsection{Seed hash}
The seed hash is different for every epoch. For the first epoch it is the Keccak-256 hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash:
\begin{equation}
 s = C_{seedhash}(\hyperlink{H i}{H_\mathbf{i}})
\end{equation}
\begin{equation}
 C_{seedhash}(\hyperlink{H i}{H_\mathbf{i}}) = \begin{cases}
\texttt{KEC}(\mathbf{0}_{32}) & \text{if} \quad E_{\mathrm{epoch}}(\hyperlink{H i}{H_\mathbf{i}}) = 0 \quad  \\
\texttt{KEC}(C_{seedhash}(\hyperlink{H i}{H_\mathbf{i}} - \hyperlink{Jepoch}{J_{\mathrm{epoch}}})) & \text{otherwise}
\end{cases}
\end{equation}
With $\mathbf{0}_{32}$ being 32 bytes of zeros.

@@

We define the array $\mathbf{c}_{i}$, consisting of 64 single bytes,  as the $i$th element of the initial cache:
\begin{equation}
 \mathbf{c}_{i} = \begin{cases}
\texttt{KEC512}(\mathbf{s}) & \text{if} \quad i = 0 \quad  \\
\texttt{KEC512}(\mathbf{c}_{i-1}) & \text{otherwise}
\end{cases}
\end{equation}
Therefore $ \mathbf{c'}$ can be defined as
\begin{equation}
 \mathbf{c'}[i] = \mathbf{c}_{i} \quad \forall \quad i < n
\end{equation}
\begin{equation}
 n = \left\lfloor\frac{c_{size}}{\hyperlink{Jhashbytes}{J_{\mathrm{hashbytes}}}}\right\rfloor
\end{equation}
The cache is calculated by performing \hyperlink{Jcacherounds}{$J_{\mathrm{cacherounds}}$} rounds of the RandMemoHash algorithm to the inital cache $\mathbf{c'}$:
\begin{equation}
 \mathbf{c} = E_{\mathrm{cacherounds}}(\mathbf{c'}, \hyperlink{Jcacherounds}{J_{\mathrm{cacherounds}}})
\end{equation}
\begin{equation}
 E_{\mathrm{cacherounds}}(\mathbf{x}, y) = \begin{cases}
\mathbf{x} & \text{if} \quad y = 0 \quad  \\
E_\text{\tiny RMH}(\mathbf{x}) & \text{if} \quad y = 1 \quad  \\
E_{\mathrm{cacherounds}}(E_\text{\tiny RMH}(\mathbf{x}), y -1 ) & \text{otherwise}
\end{cases}
\end{equation}
Where a single round modifies each subset of the cache as follows:
\begin{equation}
 E_\text{\tiny RMH}(\mathbf{x}) = \big( E_{rmh}(\mathbf{x}, 0), E_{rmh}(\mathbf{x}, 1), ... , E_{rmh}(\mathbf{x}, n - 1) \big)
\end{equation}
\hypertarget{Ecacherounds}{}
\begin{multline}
  E_{rmh}(\mathbf{x}, i) = \texttt{KEC512}(\mathbf{x'}[(i - 1 + n) \mod n] \oplus \mathbf{x'}[\mathbf{x'}[i][0] \mod n]) \\
  \text{with} \quad \mathbf{x'} = \mathbf{x} \quad \text{except} \quad \mathbf{x'}[j] = E_{rmh}(\mathbf{x}, j) \quad \forall \quad j < i
\end{multline}

@@

\subsection{Proof-of-work function}
Essentially, we maintain a "mix" \hyperlink{Jmixbytes}{$J_{\mathrm{mixbytes}}$} bytes wide, and repeatedly sequentially fetch \hyperlink{Jmixbytes}{$J_{\mathrm{mixbytes}}$} bytes from the full dataset and use the $E_\text{\tiny FNV}$ function to combine it with the mix. \hyperlink{Jmixbytes}{$J_{\mathrm{mixbytes}}$} bytes of sequential access are used so that each round of the algorithm always fetches a full page from RAM, minimizing translation lookaside buffer misses which ASICs would theoretically be able to avoid.

>>>>

The values stemming from the computation of transactions, specifically the \hyperlink{Transaction Receipt}{transaction receipts, $B_\mathbf{R}$}, and that defined through the transaction's \hyperlink{Pi}{stateR-accumulation function, $\Pi$}, are formalised later in section \ref{sec:statenoncevalidation}.

@@

The validity is determined as:
\begin{equation}
\begin{array}[t]{rcl}
S(T) & \neq & \varnothing \quad \wedge \\
\boldsymbol{\sigma}[S(T)] & \neq & \varnothing \quad \wedge \hypertarget{transaction nonce}{\\
T_\mathbf{n} & = & \boldsymbol{\sigma}[S(T)]_\mathbf{n} \quad \wedge \\}
g_0 & \leqslant & T_\mathbf{g} \quad \wedge \\
v_0 & \leqslant & \boldsymbol{\sigma}[S(T)]_\mathbf{b} \quad \wedge \\
T_\mathbf{g} & \leqslant & {B_H}_\mathbf{l} - \hyperlink{ell}{\ell}\hyperlink{R u}{(B_\mathbf{R})_\mathbf{u}}
\end{array}
\end{equation}

@@

There exists a seed which can be computed for each block by scanning through the block headers up until that point. From the seed, one can compute a pseudorandom cache, \hyperlink{Jcacheinit}{$J_{\mathrm{cacheinit}}$} bytes in initial size. Light clients store the cache. From the cache, we can generate a dataset, \hyperlink{Jdatasetinit}{$J_{\mathrm{datasetinit}}$} bytes in initial size, with the property that each item in the dataset depends on only a small number of items from the cache. Full clients and miners store the dataset. The dataset grows linearly with time.

@@

\begin{tabularx}{\textwidth}{lrX}
%\begin{tabu}{X[,l]X[,r]X[,l]} 
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{ \\
\midrule 
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word. }\hypertarget{Jdatasetinit}{ \\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. }\hypertarget{Jdatasetgrowth}{ \\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. }\hypertarget{Jcacheinit}{\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.}\hypertarget{Jcachegrowth}{\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.}\hypertarget{Jepoch}{\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.}\hypertarget{Jmixbytes}{\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.}\hypertarget{Jhashbytes}{\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.}\hypertarget{Jparents}{\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.}\hypertarget{Jcacherounds}{\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.}\hypertarget{Jaccesses}{\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.}\\
\bottomrule
%\end{tabu}
\end{tabularx}

\subsection{Size of dataset and cache}
The size for Ethash's cache $\mathbf{c} \in \mathbb{B}$  and dataset $\mathbf{d} \in \mathbb{B}$ depend on the epoch, which in turn depends on the block number.
\begin{equation}
E_{\mathrm{epoch}}(\hyperlink{H i}{H_\mathbf{i}}) = \left\lfloor\frac{\hyperlink{H i}{H_\mathbf{i}}}{\hyperlink{Jepoch}{J_{\mathrm{epoch}}}}\right\rfloor
\end{equation}
The size of the dataset growth is \hyperlink{Jdatasetgrowth}{$J_{\mathrm{datasetgrowth}}$} bytes, and the size of the cache growth is \hyperlink{Jcachegrowth}{$J_{\mathrm{cachegrowth}}$} bytes, where the growth of each occurs every epoch. In order to avoid regularity leading to cyclic behavior, the size must be a prime number. Therefore the size is reduced by a multiple of \hyperlink{Jmixbytes}{$J_{\mathrm{mixbytes}}$}, for the dataset, and \hyperlink{Jhashbytes}{$J_{\mathrm{hashbytes}}$} for the cache.\hypertarget{dsize}{
Let $d_{size} = \lVert \mathbf{d} \rVert$ be the size of the dataset. Which is calculated using:}
\begin{equation}
 d_{size} = E_{prime}(\hyperlink{Jdatasetinit}{J_{\mathrm{datasetinit}}} + \hyperlink{Jdatasetgrowth}{J_{\mathrm{datasetgrowth}}} \cdot E_{\mathrm{epoch}} - \hyperlink{Jmixbytes}{J_{\mathrm{mixbytes}}}, J_{\mathrm{mixbytes}})
\end{equation}
The size of the cache, $c_{size}$, is calculated using
\begin{equation}
 c_{size} = E_{prime}(\hyperlink{Jcacheinit}{J_{\mathrm{cacheinit}}} + \hyperlink{Jcachegrowth}{J_{\mathrm{cachegrowth}}} \cdot E_{\mathrm{epoch}} - \hyperlink{Jhashbytes}{J_{\mathrm{hashbytes}}}, J_{\mathrm{hashbytes}})
\end{equation}
\begin{equation}
 E_{prime}(x, y) = \begin{cases}
x & \text{if} \quad x / y \in \mathbb{P} \\
E_{prime}((x - 1) \cdot y, y) & \text{otherwise}
\end{cases}
\end{equation}
\subsection{Dataset generation}
In order the generate the dataset we need the cache $c$, which is an array of bytes. It depends on the cache size  $c_{size}$ and the seed hash $s \in \mathbb{B}_{32}$.
\subsubsection{Seed hash}
The seed hash is different for every epoch. For the first epoch it is the Keccak-256 hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash:
\begin{equation}
 s = C_{seedhash}(\hyperlink{H i}{H_\mathbf{i}})
\end{equation}
\begin{equation}
 C_{seedhash}(\hyperlink{H i}{H_\mathbf{i}}) = \begin{cases}
\texttt{KEC}(\mathbf{0}_{32}) & \text{if} \quad E_{\mathrm{epoch}}(\hyperlink{H i}{H_\mathbf{i}}) = 0 \quad  \\
\texttt{KEC}(C_{seedhash}(\hyperlink{H i}{H_\mathbf{i}} - \hyperlink{Jepoch}{J_{\mathrm{epoch}}})) & \text{otherwise}
\end{cases}
\end{equation}
With $\mathbf{0}_{32}$ being 32 bytes of zeros.

@@

We define the array $\mathbf{c}_{i}$, consisting of 64 single bytes,  as the $i$th element of the initial cache:
\begin{equation}
 \mathbf{c}_{i} = \begin{cases}
\texttt{KEC512}(\mathbf{s}) & \text{if} \quad i = 0 \quad  \\
\texttt{KEC512}(\mathbf{c}_{i-1}) & \text{otherwise}
\end{cases}
\end{equation}
Therefore $ \mathbf{c'}$ can be defined as
\begin{equation}
 \mathbf{c'}[i] = \mathbf{c}_{i} \quad \forall \quad i < n
\end{equation}
\begin{equation}
 n = \left\lfloor\frac{c_{size}}{\hyperlink{Jhashbytes}{J_{\mathrm{hashbytes}}}}\right\rfloor
\end{equation}
The cache is calculated by performing \hyperlink{Jcacherounds}{$J_{\mathrm{cacherounds}}$} rounds of the RandMemoHash algorithm to the inital cache $\mathbf{c'}$:
\begin{equation}
 \mathbf{c} = E_{\mathrm{cacherounds}}(\mathbf{c'}, J_{\mathrm{cacherounds}})
\end{equation}
\begin{equation}
 E_{\mathrm{cacherounds}}(\mathbf{x}, y) = \begin{cases}
\mathbf{x} & \text{if} \quad y = 0 \quad  \\
E_\text{\tiny RMH}(\mathbf{x}) & \text{if} \quad y = 1 \quad  \\
E_{\mathrm{cacherounds}}(E_\text{\tiny RMH}(\mathbf{x}), y -1 ) & \text{otherwise}
\end{cases}
\end{equation}
Where a single round modifies each subset of the cache as follows:
\begin{equation}
 E_\text{\tiny RMH}(\mathbf{x}) = \big( E_{rmh}(\mathbf{x}, 0), E_{rmh}(\mathbf{x}, 1), ... , E_{rmh}(\mathbf{x}, n - 1) \big)
\end{equation}
\hypertarget{Ecacherounds}{}
\begin{multline}
  E_{rmh}(\mathbf{x}, i) = \texttt{KEC512}(\mathbf{x'}[(i - 1 + n) \mod n] \oplus \mathbf{x'}[\mathbf{x'}[i][0] \mod n]) \\
  \text{with} \quad \mathbf{x'} = \mathbf{x} \quad \text{except} \quad \mathbf{x'}[j] = E_{rmh}(\mathbf{x}, j) \quad \forall \quad j < i
\end{multline}

@@

\subsection{Proof-of-work function}
Essentially, we maintain a "mix" \hyperlink{Jmixbytes}{$J_{\mathrm{mixbytes}}$} bytes wide, and repeatedly sequentially fetch $J_{\mathrm{mixbytes}}$ bytes from the full dataset and use the $E_\text{\tiny FNV}$ function to combine it with the mix. $J_{\mathrm{mixbytes}}$ bytes of sequential access are used so that each round of the algorithm always fetches a full page from RAM, minimizing translation lookaside buffer misses which ASICs would theoretically be able to avoid.
